Millions of Type Errors

### 2023-09-13 programming23/paper.tex
Add short bios
Not luatex
huge ctime comment (15 days), fix overlapping color boxes

\author[b]{Alan Jeffrey}
\authorinfo{(\email{ajeffrey@roblox.com}) TBD}
% \orcid{0000-0001-6342-0318}
\affiliation[b]{Roblox, San Mateo, CA, USA}

@@

\author[b]{Mitesh Shah}
\authorinfo{(\email{mshah@roblox.com}) TBD.}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}

@@

  \begin{subfigure}[t]{\columnwidth}
    %% NOTE max time = 1 million seconds = 15 days

@@

    \begin{tabular}{lr@{~}r@{~}rr@{~}r@{~}rr@{~}r@{~}r}
      & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
      & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} \\\midrule
      TypeMismatch & {0} & {0} & {0} & {159} & {62} & {129} & {21} & {10} & {28} \\
      UnknownSymbol & {0} & {0} & {0} & {2348} & {496} & {2973} & {49} & {19} & {55} \\
      UnknownProperty & {0} & {0} & {0} & {347} & {180} & {385} & {19} & {19} & {35} \\
      NotATable & {0} & {0} & {0} & {7} & {2} & {8} & {2} & {0} & {1} \\
      CannotExtendTable & {0} & {0} & {0} & {7} & {9} & {10} & {0} & {0} & {1} \\
      OnlyTablesCanHaveMethods & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      DuplicateTypeDefinition & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
      CountMismatch & {0} & {0} & {0} & {223} & {48} & {269} & {12} & {2} & {17} \\
      FunctionDoesNotTakeSelf & {0} & {0} & {0} & {4} & {6} & {5} & {0} & {0} & {0} \\
      OccursCheckFailed & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
      UnknownRequire & {0} & {0} & {0} & {91} & {39} & {85} & {12} & {3} & {4} \\
      IncorrectGenericParameterCount & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
      SyntaxError & {8349} & {314} & {19220} & {983} & {46} & {2658} & {16} & {0} & {71} \\
      UnknownPropButFoundLikeProp & {0} & {0} & {0} & {26} & {18} & {21} & {1} & {0} & {1} \\
      GenericError & {0} & {0} & {0} & {206} & {52} & {203} & {8} & {1} & {9} \\
      CannotCallNonFunction & {0} & {0} & {0} & {17} & {4} & {20} & {1} & {0} & {1} \\
      ExtraInformation & {0} & {0} & {0} & {48} & {7} & {39} & {2} & {0} & {1} \\
      ModuleHasCyclicDependency & {0} & {0} & {0} & {20} & {9} & {15} & {0} & {0} & {1} \\
      IllegalRequire & {0} & {0} & {0} & {16} & {3} & {33} & {0} & {0} & {2} \\
      FunctionExitsWithoutReturning & {0} & {0} & {0} & {9} & {3} & {6} & {11} & {5} & {8} \\
      CannotInferBinaryOperation & {0} & {0} & {0} & {1} & {2} & {1} & {7} & {6} & {9} \\
      MissingProperties & {0} & {0} & {0} & {11} & {3} & {11} & {6} & {4} & {6} \\
      OptionalValueAccess & {0} & {0} & {0} & {40} & {52} & {27} & {6} & {2} & {7} \\
      MissingUnionProperty & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      TypesAreUnrelated & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {1} \\
    \end{tabular}

@@

@@

@@

% Local Variables:
% TeX-engine: luatex
% End:

>>>>

\author[b]{Alan Jeffrey}
\authorinfo{(\email{ajeffrey@roblox.com}) is a Principal Software Engineer at Roblox.}
% \orcid{0000-0001-6342-0318}
\affiliation[b]{Roblox, San Mateo, CA, USA}

@@

\author[b]{Mitesh Shah}
\authorinfo{(\email{mshah@roblox.com}) is Senior Engineering Director, Programmability, at Roblox.}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}
\newcommand{\gbox}[1]{\colorbox{green!20}{#1}}
\newcommand{\ybox}[1]{\colorbox{yellow!18}{#1\vphantom{Ap}}}
\newcommand{\obox}[1]{\colorbox{orange!29}{#1\vphantom{Ap}}}
\newcommand{\rbox}[1]{\colorbox{red!30}{#1\vphantom{Ap}}}

@@

  \begin{subfigure}[t]{\columnwidth}
    %% NOTE max time = 1 million seconds = 15 days ...  +100 are over 2 days

@@

    \begin{tabular}{lr@{}r@{}rr@{}r@{}rr@{}r@{}r}
      & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
      & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} \\\midrule
      TypeMismatch & {0} & {0} & {0} & {159} & {62} & {129} & {21} & {10} & {28} \\
      UnknownSymbol & {0} & {0} & {0} & {2348} & {496} & {2973} & {49} & {19} & {55} \\
      UnknownProperty & {0} & {0} & {0} & {347} & {180} & {385} & {19} & {19} & {35} \\
      NotATable & {0} & {0} & {0} & {7} & {2} & {8} & {2} & {0} & {1} \\
      CannotExtendTable & {0} & {0} & {0} & {7} & {9} & {10} & {0} & {0} & {1} \\
      OnlyTablesCanHaveMethods & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      DuplicateTypeDefinition & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
      CountMismatch & {0} & {0} & {0} & {223} & {48} & {269} & {12} & {2} & {17} \\
      FunctionDoesNotTakeSelf & {0} & {0} & {0} & {4} & {6} & {5} & {0} & {0} & {0} \\
      OccursCheckFailed & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
      UnknownRequire & {0} & {0} & {0} & {91} & {39} & {85} & {12} & {3} & {4} \\
      IncorrectGenericParameterCount & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
      SyntaxError & {8349} & {314} & {19220} & {983} & {46} & {2658} & {16} & {0} & {71} \\
      UnknownPropButFoundLikeProp & {0} & {0} & {0} & {26} & {18} & {21} & {1} & {0} & {1} \\
      GenericError & {0} & {0} & {0} & {206} & {52} & {203} & {8} & {1} & {9} \\
      CannotCallNonFunction & {0} & {0} & {0} & {17} & {4} & {20} & {1} & {0} & {1} \\
      ExtraInformation & {0} & {0} & {0} & {48} & {7} & {39} & {2} & {0} & {1} \\
      ModuleHasCyclicDependency & {0} & {0} & {0} & {20} & {9} & {15} & {0} & {0} & {1} \\
      IllegalRequire & {0} & {0} & {0} & {16} & {3} & {33} & {0} & {0} & {2} \\
      FunctionExitsWithoutReturning & {0} & {0} & {0} & {9} & {3} & {6} & {11} & {5} & {8} \\
      CannotInferBinaryOperation & {0} & {0} & {0} & {1} & {2} & {1} & {7} & {6} & {9} \\
      MissingProperties & {0} & {0} & {0} & {11} & {3} & {11} & {6} & {4} & {6} \\
      OptionalValueAccess & {0} & {0} & {0} & {40} & {52} & {27} & {6} & {2} & {7} \\
      MissingUnionProperty & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      TypesAreUnrelated & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {1} \\
    \end{tabular}

@@

\Cref{f:tefs}~FILL story is edits to DM vs edits to code.
Data model awareness, call for future work.

\begin{figure}[t]
  \mnocheck{}

  \mnonstrict{}

  \mstrict{}

  \caption{Example sessions}
  \label{f:indy-session}
\end{figure}

@@

TODO correlations, compare modes!!!

@@
